Probability

### 2016-04-25 prob.tex
prob.tex \subsection{Quantum Probability Measures} delete before typing

Although it seems that we need an infinite
long table to specify the quantum probability measure~$\mu$, our $\mu$
is actually given by a simple formula~$\melement{0}{E}$. In general,
Born discovered each quantum state
$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $ induces a probability
measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$ on the space of
events defined for any event $E\in\qevents$ as
follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.\yutsung{Check!!!}
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\yutsung{...I think I need to check these properties identify an
unique Born rule in CQT or something...}

% \begin{itemize}
% \item Family I: $\proj{0}$, $\proj{1}$ 
% \item Family II: $\proj{\ps}$, $\proj{\ms}$
% \end{itemize}
% In family I, all operators can be expressed as $\left\{ \lambda_{1}\proj{0}+\lambda_{2}\proj{1}~\middle|~\lambda_{1},\lambda_{2}\in\mathbb{C}\right\} $.
% In order to identify projectors among them, we need to solve the following
% two equations.
% \begin{eqnarray*}
% \lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{*}=\lambda_{1}^{*}\proj{0}+\lambda_{2}^{*}\proj{1}\\
% \lambda_{1}\proj{0}+\lambda_{2}\proj{1} & = & \left(\lambda_{1}\proj{0}+\lambda_{2}\proj{1}\right)^{2}=\lambda_{1}^{2}\proj{0}+\lambda_{2}^{2}\proj{1}
% \end{eqnarray*}
% Therefore, we actually have $\lambda_{1},\lambda_{2}\in\left\{ 0,1\right\} $,
% and there are only four projections: $0$, $\proj{0}$, $\proj{1}$,
% and $\mathbb{1}=\proj{0}+\proj{1}$. Then, $\mu_{\ket{\ps}}$ and
% $\mu_{\ket{\ms}}$ of each projections are 
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \mu_{\ket{\ps}}(0) & = & 0\\
% \mu_{\ket{\ps}}(\proj{0}) & = & 1/2\\
% \mu_{\ket{\ps}}(\proj{1}) & = & 1/2\\
% \mu_{\ket{\ps}}(\mathbb{1}) & = & 1
% \end{array} & \begin{array}{rcl}
% \mu_{\ket{\ms}}(0) & = & 0\\
% \mu_{\ket{\ms}}(\proj{0}) & = & 1/2\\
% \mu_{\ket{\ms}}(\proj{1}) & = & 1/2\\
% \mu_{\ket{\ms}}(\mathbb{1}) & = & 1
% \end{array}\end{array}
% \]
% Similarly, $\mu_{\ket{\ps}}$ and $\mu_{\ket{\ms}}$ gives two probability
% for family II as well.
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \mu_{\ket{\ps}}(0) & = & 0\\
% \mu_{\ket{\ps}}(\proj{+}) & = & 1\\
% \mu_{\ket{\ps}}(\proj{\ms}) & = & 0\\
% \mu_{\ket{\ps}}(\mathbb{1}) & = & 1
% \end{array} & \begin{array}{rcl}
% \mu_{\ket{\ms}}(0) & = & 0\\
% \mu_{\ket{\ms}}(\proj{\ps}) & = & 0\\
% \mu_{\ket{\ms}}(\proj{\ms}) & = & 1\\
% \mu_{\ket{\ms}}(\mathbb{1}) & = & 1
% \end{array}\end{array}
% \]

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu$, our $\mu$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.\yutsung{Check!!!}
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\yutsung{...I think I need to check these properties identify an
unique Born rule in CQT or something...}

@@

\yutsung{There are three ways to characterize a quantum probability: 
\begin{enumerate}
\item The above two conditions as Gleason did. 
\item As a linear functional on a {*} algebra. 
\item As induced by a state vector by the Born rule (\ref{eq:Born}). 
\end{enumerate}
According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
the equivalence between 1. and 2. only hold for $d\ge3$ because of
Gleason' theorem. Therefore, it seems hard to get insight for how
to handle Gleason's theorem by {*}-algebra formalism...

The equivalence between 2. and 3. can be found in Proposition 4.1.1
in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
by a faithful pseudotrace $\tau$ and $\mu_{\psi}(E)=\tau\left(\proj{\psi}E\right)$.
The faithful pseudotrace is defined in section 5.2 Decomposition of
algebra with a list of conditions. The problem is:
\begin{itemize}
\item Lemma 5.2.1 proved there exists a faith pseudotrace, but said nothing
about uniqueness. Therefore, these conditions may not uniquely determine
the Born rule?
\item We don't formulate thing in algebra... So although we may have an
analog or something, we cannot quite sure our conditions will be exactly
the same as theirs. 
\end{itemize}
If we admit the above, then the condition (a) to (c) and $\tau\left(AB\right)=\tau\left(BA\right)$
implies 
\begin{itemize}
\item Our map $\tilde{\mu}:\Hilb\rightarrow\qevents\rightarrow[0,1]$ should
satisfy $\tilde{\mu}_{\psi}$ is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
\end{itemize}
The condition (a) and (d) implies
\begin{itemize}
\item Our map $\tilde{\mu}$ satisfy $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
\end{itemize}
$\tau\left(AB\right)=\tau\left(BA\right)$ also implies
\begin{itemize}
\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
Besides, the condition (a) also gives the probability of mixed states
form pure states... OK... it seems that I know what I am going to
type for DQT, but I think I need to sort them out before type them...}

% \yutsung{If we follow \cite{Maassen2010,Swart2013}, then we also
% need 
% \begin{itemize}
% \item $\mu$ can be extended to a linear functional~$\mu:alg\left(\qevents\right)\rightarrow\mathbb{C}$,
% where $alg\left(\qevents\right)$ is the minimal $*$-algebra generated
% by $\qevents$.
% \end{itemize}
% Also, 
% \begin{itemize}
% \item for all $A\in\qevents$, we have $\mu(A^{*}A)\geq0$. 
% \end{itemize}
% should be 
% \begin{itemize}
% \item for all $A\in alg\left(\qevents\right)$, we have $\mu(A^{*}A)\geq0$. 
% \end{itemize}
% because we have $\mu(A^{*}A)=\mu(A^{2})=\mu(A)$ if $A$ is a projection.}\\

% \yutsung{$\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
% is the minimal $*$-algebra generated by $P_{1},P_{2},\ldots,P_{k}$,
% but it contains all possible observables $P_{1},P_{2},\ldots,P_{k}$
% can generate (and something more) not just projections. For example,
% $2\mathbb{1}\in\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $.}\\

% \yutsung{So $\mu_{\psi}$ maps the projections generated by $P_{1},P_{2},\ldots,P_{k}$
% to $[0,1]$, and maps $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
% to $\mathbb{C}$...}\\

>>>>

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu$, our $\mu$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}

@@
